Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-22 cvpr2018.tex
8th

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We leverage the hierarchical deep representations of convolutional layers and introduce deeply-nested adversarial training to regularize the representations to be compositional for multi-scale image generation. To this end, we present a new network architecture, which is symmetric as well as extensile, to push generated images to high resolutions.  We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. Our method, at the first time, shows a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution or higher with arbitrary extensions. With extensive experimental validation on three major datasets, our method sets up a new state of the art to this field.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic high-resolution image conditional on arbitrary semantic description is a meaningful problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a vector to a RGB image space.  Differently, the vector space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be semantically consistent, i.e., the generated images not only reflect the principal concept of descriptions in global images but also can reflect the fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images. This method needs individual two-stage training, which is relatively not straightforward to be applied. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training ($128{\times}128$) image according to targeting semantic descriptions. However, the high resolution synthesis ability is still indeterminate. 
Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$) and diverse images is still an open question according to current reported studies.

We outline several empirical reasons for this challenges using GANs particularly for text-to-image synthesis. The first problem comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are many a rich number of literature trying to stabilize GAN training \cite{salimans2016improved}. But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.

With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in a fully end-to-end manner - a Vanilla fashion. The contributions are described follows.

To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical representations of convolutional layers through deeply compositional constraints. In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions. We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal.
To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.

@@

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images. Recently, Dong \etal \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions. Cha \etal \cite{dash2017tac} use the perceptional loss and Dash \etal \cite{dash2017tac} use image labels to assist GAN training.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g. training instability. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}. While our method does not use any extra information apart from input text and images. Moreover, such difficulties grow significantly as targeting image resolution increases.

@@

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators. The usage for high-resolution image is unclear \cite{han2017stackgan}. Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations for implicit subtask integration, which enables end-to-end high-resolution image synthesis.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. We introduce accompanying hierarchically-nested adversarial supervision, with a goal to enhance and regularizes layer representations to support final high resolution outputs.   
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs}
\end{figure}

@@

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
 \begin{equation}
 \label{game}
 \begin{split}
  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[\log D(x)] +  \\
					  &\mathbb{E}_{z\sim p_{z}}[\log (1-D(G(z)))]		   
 \end{split}
 \end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-\log(D(G(z)))$ rather than $\log(1-D(G(z)))$, namely, the $\log(D)$ trick.

@@

The discriminator $D$ in our model mainly consists of two branches: matching-aware pair discrimination branch $D_{pair}$, and image discrimination branch $D_{img}$, both branches share the same  image encoder.

Given a pair of image and text embedding $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer $x$  to an image code $Code_x$. $Code_x$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

@@

 Given a mini-batch of training data consists of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. First of all, we sample fakes images using $G$.
 $\hat{x_1} = G(z_1, \psi_t)$ and $\hat{x_2} = G(z_2, \psi_t)$, where $z_1$ and $z_2$ are random vector sampled from norm Gaussian distribution.

The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
					  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{t \sim p_{data}}[\log(D(\hat{x_1}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	&\mathbb{E}_{(x, t) \sim p_{data}}[\log( D( x  \psi_t) ) ] -  0.5*(\\
		  &\mathbb{E}_{(x, \hat{t}) \sim p_{data}}[\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
		  &\mathbb{E}_{t \sim p_{data}}[\log(D_{pair}(\hat{x_1}, \psi_t) ) ] + \\
		  &\mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - 0.5* ( \\
		  &\mathbb{E}[\log( D_{img}(\hat{x_1}))] + \mathbb{E}[\log( D_{img}(\hat{x_2}) )  ] )
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

@@

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.\textcolor{red}{need to change to goodfellow algorithm style}}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]

 		\For{$i \gets 1 \textrm{ to } S$ }
 		\State $z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
 		\State $\hat{x_1}, \hat{x_2} = G(z_1, \psi_t),  G(z_2, \psi_{\hat{t}})$ %\{Forward through $G$ using matching text embedding\}
 		\State $d_r$ = $D_{pair}(x, \psi_t)$ \{(real image, matching text)\}
 		\State $d_w$ = $D_{pair}(x, \psi_{\hat{t}})$ \{(real image, wrong text)\}
 		\State $d_f$ = $D_{pair}(\hat{x_1}, \psi_t)$ \{(fake image, matching text)\}
 		\State $s_r, s_1, s_2$ = $D_{img}(x), D_{img}(\hat{x_1})$, $D_{img}(\hat{x_1})$ %\{Forward through $D_{img}$ with $\hat{x_1}$\}

 		\State $loss_{img}$ = $ (\log(1-s_1) + \log(1-s_2))/2 $
 		\State $loss_{pair}$ = $ (\log(1-d_w) + \log(1-d_f))/2 $

 		\State $\mathcal{L}_{D}$ = $\log(d_r) + \log(s_r) +loss_{img} + loss_{pair}$
 		\State $\mathcal{L}_{G}$ = $\log(1-d_f) +  ( \log(1-s_1) + \log(1-s_2) )/2 $
 		\State $\theta_G$ = $\theta_G$ - ${\delta \mathcal{L}_G } / {\delta \theta_G}$  \{Update generator\}
 		\State $\theta_D$ = $\theta_D$ - ${\delta \mathcal{L}_D} / {\delta \theta_D}$  \{Update generator\}

 		\EndFor

 	\end{algorithmic}
 \end{algorithm}

%\begin{algorithm}
%	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we summarize the algorithm using SGD for simplicity.   
%		\label{alg:gan-train}}
%	\begin{algorithmic}[1]
%		\Input{sample a minibatch of images, $x$, matching text description $t$, mis-matching $\hat{t}$,
%			}
%		\For{$i \gets 1 \textrm{ to } S$}
%			$z_1, z_2 \sim \mathcal{N}(0,\bm{1})^Z$
%			\State $\hat{x_1}$=$G(z_1, \psi_t)$ \Comment{Forward through $G$ using matching text embedding}
%			\STATE {$\hat{x_2}$}{$G(z_2, \psi_\hat{t})$} \Comment{Forward through $G$ using mis-matching text embedding}
%			
%			\STATE {$d_r$}{$D_{pair}(x, \psi_t)$} \Comment{(real image, matching text)}
%			\STATE {$d_m$}{$D_{pair}(x, \psi_\hat{t})$} \Comment{(real image, mis-matching text)}
%			\STATE {$d_f$}{$D_{pair}(\hat{x_1}, \psi_t)$} \Comment{(fake image, matching text)}
%			\STATE {$s_r$}{$D_{img}(x)$} \Comment{Forward through $D_{img}$ with $x$}
%			\STATE {$s_1$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_1}$}
%			\STATE {$s_2$}{$D_{img}(\hat{x_1})$} \Comment{Forward through $D_{img}$ with $\hat{x_2}$}
%			\STATE {$\mathcal{L}_{D}$}{$(d_r-1)^2 + (s_r-1)^2 + (d_m + d_f + s_1 + s2)/2 $} 
%			\STATE {$\mathcal{L}_{G}$}{$((d_f -1)^2 + (s_1 -1)^2 + (s_2 -1)^2 $} 
%			\STATE {$\theta_G$}{$\frac{\delta \mathcal{L}_G}{\delta \theta_G}$}  \Comment{Update generator}
%			\STATE {$\theta_D$}{$\frac{\delta \mathcal{L}_D}{\delta \theta_D}$}  \Comment{Update generator}
%		\EndFor	
%	\end{algorithmic}
%\end{algorithm}

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
\begin{document}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks.  We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. To our best knowledge, our method is the first to show a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution. With extensive experimental validation on three major datasets, our method significantly improves previous method and sets up a new state of the art to this field.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic high-resolution image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve the principal concept of descriptions generally but also preserve the fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256{\times}256$) and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators. There are a rich number of literature tacking this issue \cite{salimans2016improved,huang2016stacked}. For text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients and needs careful consideration. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators.

%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.

With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner. The contributions are described follows.

To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is simply motivated by two intuitions. 
We hope feature maps in different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions and maximize the implicit effectiveness of feature representations.
We introduce accompanying hierarchically-nested adversarial objective at intermediate layers to achieve this goal. To better cooperate with discriminators, we present an quite intuitive network structure design to encourage more efficient and effective training.

@@

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
Deep generative models grows wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many not well-solved difficulties, e.g. training instability. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}. While our method does not use any extra information apart from input text. Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.

@@

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Compared with these strategies that progressively train low- to high-resolution GANs, our method takes advantages of multi-level representations that encourages implicit subtask integration, which enables end-to-end high-resolution image synthesis.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.   
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs}
\end{figure}

@@

\section{Preliminary}
\subsection{Generative Adversary Network}
Generative adversary networks (GANs) are composed of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other in a two-player minimax game. The discriminator $D$ is optimized to distinguish the synthesized images from the real images, meanwhile, the generator $G$ is trained to fool the discriminator by trying to convert an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $V(D, G)$,
 \begin{equation}
 \label{game}
 \begin{split}
  \underset{G}{\min}\ \underset{D}{\max}\ V(D, G) =  &\mathbb{E}_{x\sim p_{data}}[log D(x)] +  \\
					  &\mathbb{E}_{z\sim p_{z}}[log (1-D(G(z)))]		   
 \end{split}
 \end{equation}
where $x$ is a real image sampled from the true data distribution $p_{data}$, $z$ is a noise vector usually sampled from some predefined distribution $p_{z}$ (e.g., Gaussian distribution).
In practice, It's been shown to work better for the generator $G$ to minimizing $-log(D(G(z)))$ rather than $log(1-D(G(z)))$, namely, the $log(D)$ trick.

@@

Given a pair of image and text embedding pair $(x, \psi{t})$ as input, in the discriminator $D$, we first transfer the $x$  to an image code $Code(x)$. $Code(x)$ along with $f_{sent}(\psi_t)$ is concatenated and fed to the matching aware branch to compute a final scale value indicating the probability of the pair being real or fake, where $f_{sent}$ consists of one linear layer and one leaky ReLU transformation,  the matching-aware branch is a set of residual blocks with strid-2 convolution, more details of the architecture will be provided in the appendix. Besides that, the image code is also fed to an image-disc branch, whose structure is very similar to the matching-aware branch, to judge the probability of the input image being real or fake. We performance batch normalization on all convolutional layers. \textcolor{red}{like stackgan, I will add much more architecture details later}

@@

 Given an input consisting of a mini-batch of images $x$ and the corresponding text $t$, mismatching text $\hat{t}$. 
 The loss function of the matching aware discriminator are summarized as:
  \begin{equation}
  \label{matchignloss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D( x,  \psi_t) ) ] +  0.5*(\\
					  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D(x, \psi_{\hat{t}} )  ] +\\
					  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D(\hat{x}, \psi_t) ) ] 
  \end{split}
  \end{equation}
This loss explicit force the discriminator to differentiate correct pair from the wrong pair.  However, there is no explicit loss that push the discriminator to differentiate real images from the fake images. The way that they formulate all the task into pair based solution complicate the task of the generator. In this paper, we propose to directly add another loss that concentrate the image quality only beside the matching loss. Specifically, it can be given by:
  \begin{equation}
  \label{discoss}
  \begin{split}
  \mathcal{L}_D = 	  &\mathbb{E}_{x, t \sim p_{data}}[\log( D_{pair}( x,  \psi_t) ) ] + 0.5*( \\
  &\mathbb{E}_{x, \hat{t} \sim p_{data}}[-\log(D_{pair}(x, \psi_{\hat{t}} )  ] +\\
  &   \mathbb{E}_{\hat{x}, t \sim p_{data}}[-\log(D_{pair}(\hat{x}, \psi_t) ) ] + \\
  & \mathbb{E}_{x \sim p_{data}}[\log( D_{img}(x) )] - \\
  & \mathbb{E}_{t \sim p_{data}}[\log( D_{img}(\hat{x}) )]
  \end{split}
  \end{equation}
\textcolor{red}{equations needs to be verified, just a rough place holder}

@@

\begin{algorithm}
	\caption{Counting mismatches between two packed \DNA{} strings
		\label{alg:packed-dna-hamming}}
	\begin{algorithmic}[1]
		\Require{$x$ and $y$ are packed \DNA{} strings of equal length $n$}
		\Statex
		\Function{Distance}{$x, y$}
		\Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
		\Let{$\delta$}{$0$}
		\For{$i \gets 1 \textrm{ to } n$}
			\If{$z_i \neq 0$}
				\Let{$\delta$}{$\delta + 1$}
			\EndIf
		\EndFor
		\State \Return{$\delta$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}
